**Density Dependence**

### 2023-02-07 Rmd/runDD.Rmd
tidy up

plot(eq,refpt="msy")
```

**Figure `r iFig=iFig+1; iFig`** Equilibrium dynamics

@@

plot(om)
```

**Figure `r iFig=iFig+1; iFig`** Time series dynamics

```{r}
plot(qmin(qmax(0.96*biomass(eq)%/%biomass(eq)[,14],0.5),1.5))+
  scale_y_continuous(labels = scales::percent)+
  geom_vline(aes(xintercept=14),col="red")+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```

>>>>

p1=plot(eq,refpt="msy")
```

@@

p2=plot(om)
```

```{r, eval=FALSE}
plot(qmin(qmax(0.96*biomass(eq)%/%biomass(eq)[,14],0.5),1.5))+
  scale_y_continuous(labels = scales::percent)+
  geom_vline(aes(xintercept=14),col="red")+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```
